\section{SYSTEM}
\label{SYSTEM}
\begin{ipifield}{}%
{This is the class which holds all the data which represents a single state of the system.}%
{}%
{\ipiitem{prefix}%
{Prepend this string to output files generated for this system. }%
{default: `'; data type: string; }%
}
\begin{ipifield}{\hyperref[CELL]{cell}}%
{Deals with the cell parameters. Takes as array which can be used to initialize the cell vector matrix.}%
{dimension: length; default: 
      [0. 0. 0. 0. 0. 0. 0. 0. 0.]; data type: float; }%
{\ipiitem{units}%
{The units the input data is given in.}%
{default: `automatic'; data type: string; }%
\ipiitem{shape}%
{The shape of the array.}%
{default:  (3, 3) ; data type: tuple; }%
\ipiitem{mode}%
{If 'mode' is 'manual', then the array is read from the content of 'cell' takes a 9-elements vector containing the cell matrix (row-major). If 'mode' is 'abcABC', then 'cell' takes an array of 6 floats, the first three being the length of the sides of the system parallelopiped, and the last three being the angles (in degrees) between those sides. Angle A corresponds to the angle between sides b and c, and so on for B and C. If mode is 'abc', then this is the same as for 'abcABC', but the cell is assumed to be orthorhombic. 'pdb' and 'chk' read the cell from a PDB or a checkpoint file, respectively.}%
{default: `manual'; data type: string; options: `manual', `file'; }%
}
\end{ipifield}
\begin{ipifield}{\hyperref[MOTION]{motion}}%
{Allow chosing the type of calculation to be performed. Holds all the information that is calculation specific, such as geometry optimization parameters, etc.}%
{}%
{\ipiitem{mode}%
{How atoms should be moved at each step in the simulatio. 'replay' means that a simulation is restarted from a previous simulation.}%
{data type: string; options: `vibrations', `minimize', `replay', `neb', `dynamics', `alchemy', `instanton', `dummy', `multi'; }%
}
\end{ipifield}
\begin{ipifield}{\hyperref[BEADS]{beads}}%
{Describes the bead configurations in a path integral simulation.}%
{}%
{\ipiitem{natoms}%
{The number of atoms.}%
{default:  0 ; data type: integer; }%
\ipiitem{nbeads}%
{The number of beads.}%
{default:  0 ; data type: integer; }%
}
\end{ipifield}
\begin{ipifield}{\hyperref[FORCES]{forces}}%
{Deals with creating all the necessary forcefield objects.}%
{}%
{}
\end{ipifield}
\begin{ipifield}{\hyperref[NORMALMODES]{normal\_modes}}%
{Deals with the normal mode transformations, including the adjustment of bead masses to give the desired ring polymer normal mode frequencies if appropriate. Takes as arguments frequencies, of which different numbers must be specified and which are used to scale the normal mode frequencies in different ways depending on which 'mode' is specified.}%
{}%
{\ipiitem{transform}%
{Specifies whether to calculate the normal mode transform using a fast Fourier transform or a matrix multiplication. For small numbers of beads the matrix multiplication may be faster.}%
{default: `fft'; data type: string; options: `fft', `matrix'; }%
}
\end{ipifield}
\begin{ipifield}{\hyperref[INITIALIZER]{initialize}}%
{Specifies the number of beads, and how the system should be initialized.}%
{}%
{\ipiitem{nbeads}%
{The number of beads. Will override any provision from inside the initializer. A ring polymer contraction scheme is used to scale down the number of beads if required. If instead the number of beads is scaled up, higher normal modes will be initialized to zero.}%
{data type: integer; }%
}
\end{ipifield}
\begin{ipifield}{\hyperref[ENSEMBLE]{ensemble}}%
{Holds all the information that is ensemble specific, such as the temperature and the external pressure.}%
{}%
{}
\end{ipifield}
\end{ipifield}
